Extending K-Means Clustering with Ptolemy’s Inequality \thanks{This work is partly funded by DFG grant No. 454630593: EPIX – Efficient Ptolemaic Indexing.}

### 2025-01-14 paper/content/5_results.tex
fix: speedup defined the wrong way around
fix figure description

In \autoref{fig:combined},
we report our results in the form of speedups,
i.e. as the number of distances calculated by our extension,
divided by the number of distances calculated by Elkan's algorithm.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{fig/combined_plot.pdf}
	\caption{
		Relative improvement in the number distance evaluations, compared to Elkan's algorithm.
        A speedup of $>1$ indicates an improvement over Elkan's original algorithm.
		\textbf{Top and middle row:} Performance increases on synthetic data generated from Gaussian (top) and uniformly random (middle) distributions.
		The dimensionality of the dataset increases left-to-right.
		\textbf{Bottom row:} Performance increases on the real-world datasets Iris (left) and Wine (right).
	}
	\label{fig:combined}
\end{figure}

>>>>

In \autoref{fig:combined},
we report our results in the form of speedups,
i.e. as the number of distances calculated by Elkan's algorithm,
divided by the number of distances  calculated by our extension.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{fig/combined_plot.pdf}
	\caption{
		Relative improvement in the number distance evaluations, compared to Elkan's algorithm.
        A speedup of $>1$ indicates an improvement over Elkan's original algorithm.
		\textbf{Top row:} Performance increases on the real-world datasets Iris (left) and Wine (center).
		\textbf{Center and bottom row:} Performance increases on synthetic data generated from Gaussian (center row) and uniformly random (bottom row) distributions.
		The dimensionality of the dataset increases left-to-right.
	}
	\label{fig:combined}
\end{figure}
